%-------------------------
% Resume in Latex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{graphicx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins (slightly tighter but safe)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}
\raggedbottom
\raggedright

% Tight spacing
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\tabcolsep}{0in}

% Section formatting (compressed)
\titleformat{\section}
  {\vspace{-6pt}\scshape\raggedright\large}
  {}{0em}{}
  [\color{black}\titlerule \vspace{-8pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-4pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \href{#2}{Visit Live} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}


\begin{center}
    {\Huge \textbf{Siddhant Jain}} \\ \vspace{6pt}
    +91 6232799390 $|$
    \href{https://coolsid.tech}{coolsid.tech} $|$
    \href{https://www.linkedin.com/in/siddhant-jain-coolsidofficial/}{linkedin.com/in/siddhant-jain-coolsidofficial} $|$
    \href{https://github.com/CoolSidOfficial}{github.com/CoolSidOfficial} $|$
    \href{mailto:siddhantjainmvm@gmail.com}{siddhantjainmvm@gmail.com}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{LNCT Group of Colleges (LNCTE)}{Nov 2022 -- Jul 2026}
{B.Tech. in Computer Science}{Bhopal, MP}
\resumeSubHeadingListEnd

\section{Technical Skills}
% SKILLS_START
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Frontend:} React, Next.js, TypeScript, Tailwind CSS, JavaScript
    \item \textbf{Backend:} FastAPI, Node.js + Express, Flask, Python, REST APIs, JWT Authentication
    \item \textbf{Databases:} PostgreSQL, MongoDB, Redis
    \item \textbf{ML \& AI Tools:} Scikit-Learn, Pandas, LangChain, Ollama
    \item \textbf{DevOps \& Infra:} Docker, Nginx, Azure, WebSockets
\end{itemize}
% SKILLS_END

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Full Stack Developer Intern}{Sep 2023 -- Apr 2024}
{AICTE IDEALAB, Bhopal, MP}{}
\begin{itemize}[leftmargin=0.15in]
    \resumeItem{Built a responsive full-stack web application using \textbf{Next.js} and \textbf{Tailwind CSS} with secure backend integration.}
    \resumeItem{Designed and implemented a secure admin panel with \textbf{JWT} authentication and \textbf{CSRF} protection.}
    \resumeItem{Developed and integrated a dynamic image gallery that increased student engagement on the platform.}
\end{itemize}

\resumeSubheading
{Frontend Developer Intern}{Apr 2023 -- Sep 2023}
{KLIC Kalchuri Incubation Center, Bhopal, MP}{}
\begin{itemize}[leftmargin=0.15in]
    \resumeItem{Delivered 5+ production-ready frontend websites using \textbf{React} and modern UI/UX practices.}
    \resumeItem{Achieved full mobile responsiveness across all projects, improving user experience on desktop and mobile.}
    \resumeItem{Collaborated directly with the Apeiro Medica team in the Dare to Start program to ship user-focused interfaces under tight deadlines.}
\end{itemize}

\resumeSubHeadingListEnd
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{CoolGuide $|$ \emph{FastAPI, Next.js, Zustand, Scikit-learn, Express.js, MongoDB, Socket.IO}}
{https://github.com/CoolSidOfficial/CoolGuide}
\begin{itemize}[leftmargin=0.15in]
    \resumeItem{Architected full-stack electronics recommendation platform handling \textbf{100+} listings with API responses under \textbf{200ms}.}
    \resumeItem{Built similarity-based recommendation engine using Scikit-learn that generates personalized top-k suggestions in real-time.}
    \resumeItem{Implemented live chat with sub-\textbf{100ms} latency using Socket.IO and deployed on Azure with Nginx reverse proxy.}
\end{itemize}

\resumeProjectHeading
{KNNFitSense $|$ \emph{React, Flask, Scikit-learn, Tailwind CSS, JavaScript}}
{https://github.com/CoolSidOfficial/KNNFitSense}
\begin{itemize}[leftmargin=0.15in]
    \resumeItem{Engineered full-stack fitness prediction platform integrating \textbf{K-Nearest Neighbors} classifier with Flask REST API and React frontend.}
    \resumeItem{Performed feature preprocessing and normalization on health metrics, delivering real-time predictions under \textbf{100ms}.}
    \resumeItem{Designed dynamic UI that renders instant results for workout and diet recommendations.}
\end{itemize}

\resumeProjectHeading
{Coolforums $|$ \emph{Next.js, Express.js, PostgreSQL, WebSockets, Docker, Redis}}
{https://github.com/CoolSidOfficial/FORUMS}
\begin{itemize}[leftmargin=0.15in]
    \resumeItem{Architected scalable full-stack discussion platform with nested replies, upvote ranking, and real-time notifications.}
    \resumeItem{Implemented WebSockets + Redis pub/sub for live comment updates and topic-based threading.}
    \resumeItem{Containerized entire application with Docker for consistent deployment and scalability.}
\end{itemize}

\resumeProjectHeading
{CoolCounsel $|$ \emph{React, Express.js, MongoDB}}
{https://coolcounsel.netlify.app/}
\begin{itemize}[leftmargin=0.15in]
    \resumeItem{Built full-stack college admission predictor for Madhya Pradesh by analyzing \textbf{10,000+} historical DTE records.}
    \resumeItem{Achieved \textbf{90\%+} prediction accuracy, helping \textbf{1,000+} students choose suitable colleges and courses.}
\end{itemize}
\resumeSubHeadingListEnd
\section{Achievements}
\resumeSubHeadingListStart

\resumeItem{Solved \textbf{200+} DSA questions, building strong problem-solving skills for scalable full-stack systems.}
\resumeItem{Built \textbf{22+} hands-on full-stack and ML projects with real-world impact and production deployments.}
\resumeItem{Semi-Finalist, Smart India Hackathon 2023 \& 2024 – Led teams building GeoTrack and Legal Gyaan using React Native, WebSockets, GPS, Node.js, MongoDB, and NLP.}

\resumeSubHeadingListEnd
\end{document}